### A. Retrieve and Set Your Working Directory

```{r, results = 'hide'}
rm(list = ls())
getwd()
setwd("~/GitHub/soil_traits/taxran")
```

### B. Load Data, Source File, and Package

```{r}
# Load Trait and Taxonomy Data
data <- read.csv("data/nestedfinal.csv")

# Load Source File
source("taxran15.R")

# Load `lme4`
# require("lme4")
require("nlme")
```

### C. Run `taxran` for a single trait

```{r}
# Assign `input` and `trait` as variables
input <- data
trait <- "Optimum"

# Note: This Can Take a Long Time, But You Can Change `n` in taxran15.R and Reload Source
#ans <- taxran15(input = data, trait = data[,"Optimum"])
ans <- taxran15(input, trait)
```

### D. Interpreting `taxran` output
The `taxran` function returns a list containing two items. 
The first is the proportion of variation explained for each taxonomic level (ans$act.pct).

```{r}
ans[[1]]
```

The second item in the `taxran` output list is the proportion of variation explained at each taxonomic level for the randomized data (ans$sim.pct). 

```{r}
ans[[2]]
```

Last, test whether or not the observed variance explained for a given taxonomic level is different from what we would expect from the randomized data:

```{r}
# Identify Taxonomic Level
tax.level <- "Family"

# Observed Variance Explained
obs.var <- ans[[1]][tax.level]

# Lower and Upper 95% Confidence Intervals
rand.var <- sort(ans[[2]][tax.level,])[c(25,975)]

# Does Observed Value Fall Within 95% Confidence Intervals?
CI.test <- obs.var > rand.var[1] && obs.var < rand.var[2] 

# Calculate a 1-Sided P-value
p.val <- max(which(sort(ans[[2]][tax.level,]) > obs.var), 0) / 1000
``` 
