### A. Retrieve and Set Your Working Directory

```{r, results = 'hide'}
# Clear objects in your environment
rm(list = ls())

# Get your working directory 
getwd()

# Set your working directory
setwd("~/GitHub/soil_traits/taxran")
```

### B. Load Data, Source File, and Package

```{r}
# Load trait and taxonomy dataframe
data <- read.csv("data/nestedfinal.csv")

# Load source file
source("taxran15.R")

# Load `nlme` package
require("nlme")
```

### C. Run `taxran` for a single trait

```{r}
# Assign `input` and `trait` as variables
input <- data
trait <- "Optimum"

# Note: this can take a long time, but you can change `n` in taxran15.R and reload source
ans <- taxran15(input, trait)
```

### D. Interpreting `taxran` output
The `taxran` function returns a list containing two items. 
The first is the proportion of variation explained for each taxonomic level (`ans$act.pct`).

```{r}
ans[[1]]
```

The second item in the `taxran` output list is the proportion of variation explained at each taxonomic level for the randomized data (`ans$sim.pct`). 

```{r}
ans[[2]]
```

Last, we can test whether or not the observed variance explained for a given taxonomic level is different from what we would expect based on the null expectaion from randomized data:

```{r}
# Identify taxonomic Level
tax.level <- "Family"

# Observed variance explained
obs.var <- ans[[1]][tax.level]

# Lower and upper 95% confidence entervals
# Note: code below based on 1000 resamplings
# Note: distribution of variance may not be normally distributed
rand.var <- sort(ans[[2]][tax.level,])[c(25,975)]
error <- qnorm(0.975)*s/sqrt(n)

# Does observed value fall within 95% confidence intervals?
CI.test <- obs.var > rand.var[1] && obs.var < rand.var[2] 

# Calculate a 1-Sided P-value
p.val <- max(which(sort(ans[[2]][tax.level,]) > obs.var), 0) / 1000
``` 
