### A. Retrieve and Set Your Working Directory

```{r, results = 'hide'}
rm(list = ls())
getwd()
setwd("~/GitHub/soil_traits/taxran")
```

### B. Load Pakcages, Data, Source File

```{r}
# Load Trait and Taxonomy Data
data <- read.csv("data/nestedfinal.csv")

# Load Source File
source("taxran15.R")

# Load `lme4`
require("lme4")
```

### C. Run `taxran` for Optimum

```{r}
# Note: This May Take Hours
ans <- taxran15(data,"Optimum")
```

### D. Interpreting `taxran` Output
The `taxran` function returns a list containing two items. 
The first is the proportion of variation explained for each taxonomic level.

```{r}
ans[[1]]
```

The second item in the `taxran` output list is the proportion of variation explained at each taxonomic level for the randomized data. 

```{r}
ans[[2]]
```

Last, let's test whether or not the observed variance explained for a given taxonomic level is different than what we would expect from randomized data:

```{r}
# Identify Taxonomic Level
tax.level <- "Family"

# Observed Variance Explained
obs.var <- ans[[1]][tax.level]

# Lower and Upper 95% Confidence Interval
rand.var <- sort(ans[[2]][tax.level,])[c(25,975)]

# Does Observed Value Fall Within 95% Confidence Intervals?
CI.test <- obs.var > rand.var[1] && obs.var < rand.var[2] 

# Calculate a 1-Sided P-value
p.val <- max(which(sort(ans[[2]][tax.level,]) > obs.var), 0) / 1000
``` 
